The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-20 project/paper/method-of-moments.tex
Addressed other suggested revisions.

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
and third moments about the mean of $B$ and $Y$.

\subsection{The Moments of the Binomial}

Let's start with the binomial. The first two moments are simply the mean and
variance, which we can state from memory:

@@

Having these, we can easily find

@@

which we will need for the third moment. We will also need $E(B^3)$, which we
will get via the third factorial moment:

@@

Now, finally, we have all the building blocks necessary to obtain the third
moment:

@@

\subsection{The Moments of the Skew Normal}

Now we'll take a look at the moments of the skew normal. Equation
\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
third moment is a little more complicated:

@@

\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}

Now we can set the moments of our two distributions equal to each other and,
taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$:

@@

Finally, one last consideration that bears mentioning is that the skew-normal
approximation will sometimes provide us with parameters that violate our
intuition. In particular, for small $p$ and $n$, equation \eqref{eq:mu-solved}
can yield negative values of $\mu$, which is impossible for the binomial. This
can be explained by the fact that as $n$ and $p$ grow more extreme, so does the
inaccuracy of our approximation. Rather than impose a hard restriction on these
cases, we would simply advise that the reader be aware of the limits of the
skew-normal and, if more accuracy is necessary, seek another method of
approximation.

>>>>

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
and third central moments of $B$ and $Y$.

\subsection{The Central Moments of the Binomial}

Let's start with the binomial. The first two central moments are simply the
mean and variance, which we can state from memory:

@@

Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
[E(B)]^2$ and thus

@@

a fact we will need for the third central moment. We will also need $E(B^3)$,
which we will get via the third factorial moment:

@@

Now, finally, we have all the building blocks necessary to obtain the third
central moment:

@@

\subsection{The Central Moments of the Skew Normal}

Now we'll take a look at the skew normal. Equation
\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
third central moment is a little more complicated:

@@

\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}
\label{subsec:solving-for-mu-sigma-lambda}

To derive our approximation, we set the central moments of our two
distributions equal to each other and, taking $n$ and $p$ as constants, solve
for $\mu$, $\sigma$ and $\lambda$:

@@

Finally, one last consideration that bears mentioning is that the skew-normal
approximation will sometimes give us parameters that violate our intuition. In
particular, for small $p$ and $n$, equation \eqref{eq:mu-solved} can yield
negative values of $\mu$, which is impossible for the binomial. This can be
explained by the fact that as $n$ and $p$ grow more extreme, so does the
inaccuracy of our approximation. Rather than impose a hard restriction on these
cases, we would simply advise that the reader be aware of the limits of the
skew-normal and, if more accuracy is necessary, seek another method of
approximation.
